
The effects of binary systems have long been a missing ingredient in equilibrium mass models of
globular clusters. Due to the effects of mass segregation, heavy binaries will quickly become
centrally concentrated, much like heavy remnants. A centrally concentrated population of heavy
binary systems could emulate the effects of heavy remnants in the central regions of a cluster and
thus by ignoring their effects the remnant populations that we infer for these cluster might be
biased.

To investigate this effect we have developed a method to include realistic binary populations in
\code{LIMEPY} models. We used this method to fit three sets of models to observations of the
globular cluster 47\,Tuc, a set with no binaries, a set with a binary fraction of $2\%$, and a set
with a binary fraction of $10\%$. Despite their different binary fractions, all three sets of models
were able to satisfyingly reproduce all observables and recovered the same structural parameters for
the models. The three sets of models differed primarily in their recovered mass functions and black
hole content. As more binaries are added, fewer high-mass remnants are required to reproduce the
kinematics of the cluster. This results in a lowered $\alpha_3$ parameter and less mass in black
holes and other heavy remnants.

We further showed how binaries fill the same role as heavy remnants in the central mass distribution
of the cluster, explaining why adding binaries to a model reduces the need for heavy remnants.

The implications of this work depend on the binary fraction of the cluster in question. For 47\,Tuc,
our best estimates place the binary fraction at around $2\%$, so this effect is likely negligible.
If however, future observations or models suggest that 47\,Tuc might be host to more binaries, then
it is important that future studies include their effects in their models if they wish to recover
accurate remnant populations.


More generally, for clusters where we expect a high binary fraction like, for example, NGC\,3201,
binaries should certainly be included in any attempts to model the mass distribution of the cluster,
especially if the goal is to constrain the population of heavy remnants within the cluster.



\section{Future Work}



In this work, we only considered binaries made up of two main sequence stars. In reality, binaries
can be formed from any cluster members and binaries where one or both components are heavy remnants
would have an even larger effect on the kinematics of the cluster then main-sequence binaries. The
reason we did not consider this class of binaries in this project is because we have essentially no
constraints on what these populations might look like. The usual photometric methods cannot be used
because there is at most one main-sequence star and radial velocity searches will only uncover them
if the binary contains a bright star. It's possible that in this case, we could turn to N-body or
Monte Carlo models to constrain the present-day remnant binary populations, but the binary
populations in these models are likely to be highly dependent on the primordial binary population
and initial conditions of the models.

In the future it would be a interesting application of this method to examine a cluster like
NGC\,3201 where we know there is likely to be a fairly large binary population. This might allow us
to place stringent and reliable constraints on the black hole population in NGC\,3201 while
accounting for the degeneracy between black hole content and mass in binaries that we have
demonstrated can be important using 47\,Tuc as a test case.